---
title: "Sandbox"
output: html_document
---

```{r setup, include=FALSE}
# Load packages
library(tidyverse)

# Set reticulate environment
library(reticulate)
use_condaenv("r-reticulate-mne", required = TRUE)

# Load mtcars dataset
data("mtcars")

# Set knitr chunk options
knitr::opts_chunk$set(echo = TRUE)
```

This is a sandbox to play around with the `reticulate` R package in order to learn Python and its interactions with R.

# Installing packages with Conda

Packages can be installed with Conda using the `reticulate::conda_install()` command:

```{r eval=FALSE}
reticulate::conda_install(packages = "pandas")
```

# Running Python code

Python code can be run within a `python` code chunk. Objects created within the R environment can be accessed in a Python code chunk using `r.`.

```{python}
import pandas

print(r.mtcars.head())
```

# MNE tutorial

The following code comes from the [Overview of MEG/EEG analysis with MNE-Python](https://mne.tools/stable/auto_tutorials/intro/plot_10_overview.html#sphx-glr-auto-tutorials-intro-plot-10-overview-py) tutorial.

## Loading data

This tutorial uses an example dataset called “Sample” which contains EEG and MEG data from one subject performing an audiovisual experiment, along with structural MRI scans for that subject.

```{python loading data}
import os
import numpy as np
import mne

# Get path to mne sample data folder
sample_data_folder = mne.datasets.sample.data_path()

# Get path to sample data for tutorial
sample_data_raw_file = os.path.join(sample_data_folder, 'MEG', 'sample',
                                    'sample_audvis_filt-0-40_raw.fif')

# Read FIF data
raw = mne.io.read_raw_fif(sample_data_raw_file)
```

You can get the basic details of a `Raw` object by printing it.

```{python}
print(raw)
```

More details are available by printing a `Raw` object's info attribute. The info attribute is a dictionary-like object that is preserved across Raw, Epochs, and Evoked objects; its data structure keeps track of channel locations, applied filters, projectors, and so forth.

```{python}
print(raw.info)
```

You can also convert a `Raw` object to a data frame with `to_data_frame()`.

```{python}
df_raw = raw.to_data_frame(long_format = True)
```

Data frames created in Python can also be accessed in R using the `py` object exported by `reticulate`.

```{r}
head(py$df_raw)
```

### Plotting

`Raw` objects also have several built-in plotting methods. `plot_psd()` shows the power spectral density (PSD) for each sensor type. `plot()` plots raw sensor traces and is interactive, allowing scrolling, scaling, bad channel marking, annotation, projector toggling, etc. (but only in interactive Python sessions).

```{python}
raw.plot_psd(fmax=50)
raw.plot(duration=5, n_channels=30)
```

These plots can be shown in the RStudio viewer pane by calling `plt.show()`.

```{python, eval=FALSE}
import matplotlib.pyplot as plt

raw.plot_psd(fmax=50)
plt.show()
```

## Preprocessing
